\documentclass[12pt, letterpaper]{article}
\usepackage{fontspec}
\usepackage{amsmath}
\usepackage[]{hyperref} % hidelinks adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,% false: boxed; true: colored links
	linkcolor=blue,% color of internal links
	citecolor=blue,% color of links to bibliography
	filecolor=blue,% color of file links
	urlcolor=blue% color of URLs
}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{hoffset=0pt, textwidth=450pt, textheight=9in, marginparwidth=100in}
\setlength\parindent{0in}

\usepackage{libertine,libertinust1math} % use Libertine font
%\usepackage{ebgaramond} % use Garamond
%\usepackage{mathpazo} % use Palatino font
%\usepackage{cochineal} % use Cochineal font
%\usepackage{newtxtext,newtxmath} % use Time News Roman font
%\usepackage{fourier} % use fourier font, good w math
%\usepackage[math]{iwona} % use iwona font, good w math

% CUSTOM COMMANDS
\newcommand{\doi}[1]{\href{#1}{{[doi]}}}
\newcommand{\preprint}[1]{\href{#1}{{[pre-print]}}}
\newcommand{\media}[1]{\href{#1}{{[media]}}}

% MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\normalsize #1}}
\setlength{\marginparsep}{10pt}
\reversemarginpar

%\usepackage{setspace}
%\setstretch{1.25}

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem} 
\sectionfont{\bfseries\Large\scshape}
\subsectionfont{\bfseries\normalsize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Title
\begin{flushright}
\footnotesize
3620 Walnut St\\
Philadelphia, PA 19104\\
Email: \href{mailto:alvinyxz@upenn.edu}{alvinyxz@upenn.edu}\\
Website: \href{https://alvinyxz.me}{alvinyxz.me}\\
\href{https://scholar.google.com/citations?user=_gHXwrsAAAAJ&hl=en}{Google Scholar} | \href{https://osf.io/utdaf/}{OSF} | \href{https://publons.com/researcher/1698569/alvin-zhou/}{Publon} | \href{https://twitter.com/alvinyxz}{Twitter}
\end{flushright}
\noindent{\LARGE\bfseries\scshape Alvin Zhou} \hfill \footnotesize Updated: December 2020
\bigskip
\hrule
\normalsize

% Education
\section*{Education}

\subsection*{University of Pennsylvania}

  \years{Ex. 2022} Ph.D. in Communication, The Annenberg School\\
%  \years{} \hspace*{2em} \textit{Concentration: Digital Media \& Social Networks}\\
%  \years{} \hspace*{2em} \textit{Advisor: Sandra González-Bailón}\\
%  \years{} \hspace*{2em} \textit{Readers: Yphtach Lelkes \& Michael X. Delli Carpini}\\
  \years{2020} M.A. in Statistics, The Wharton School\\
  \years{2019} M.A. in Communication, The Annenberg School

\subsection*{University of Southern California}

  \years{2017}M.A. in Strategic Public Relations, The Annenberg School
%  \years{} \textit{Director’s Award for Excellence}}\\
%  \years{} \hspace*{2em} \textit{Thesis: Public Relations as a Diversity Management Approach}\\
%  \years{} \hspace*{2em} \textit{Advisor: Aimei Yang}\\
%  \years{} \hspace*{2em} \textit{Readers: Robert Kozinets \& Larry Gross}\\
  
\subsection*{Tsinghua University}

  \years{2015} B.Eng. in Mechanical Engineering\\
  \years{2015} B.A. in Journalism

% Research Areas
\section*{Research Areas}
  \years{-} Computational Social Science: Digital Media, Social Networks, Communication as Design\\
  \years{-} Strategic Communication: Public Relations, Network Ecology, Public-Public Relationships\\
  \years{-} Political Communication: Audience Behavior, News Consumption, Ideological Segregation

% Awards and Honors
\section*{Awards and Honors}

\subsection*{Academic Research Awards and Honors}

  \years{2020} PRIDE Article of the Year Award, Public Relations Division, NCA\\
  \years{2020} Page Legacy Scholar, The Arthur W. Page Center\\
  \years{2019} Robert Heath Award, Public Relations Division, ICA\\
  \years{2019} Top Faculty Paper Award, 1$^{st}$ Place, Public Relations Division, ICA\\
  \years{2018} Top Student Paper Award, 1$^{st}$ Place, Public Relations Division, NCA\\
  \years{2017-22} Annenberg Summer Fellowship, University of Pennsylvania\\
  \years{2017-22} Annenberg Research/Teaching Fellowship, University of Pennsylvania\\
  \years{2017} Director's Award for Excellence, University of Southern California\\
  \years{2016} Top Student Paper Award, 3$^{rd}$ Place, Public Relations Division, NCA\\

\subsection*{Travel and Other Awards and Honors}

  \years{2020} Student Travel Grant, International Communication Association\\
  \years{2019-22} GAPSA Student Travel Grant, University of Pennsylvania\\
  \years{2019} Prestage-Cook Travel Award, Southern Political Science Association\\
  \years{2019} Student Travel Grant, ICA Computational Methods Interest Group\\
  \years{2017} Student Travel Grant, International Communication Association\\
  \years{2016} GSG Student Travel Grant, University of Southern California\\
  \years{2014} Student Leadership Award, Tsinghua University\\
  \years{2013} Silver Award, College Student Physics Competition, Chinese Physical Society

% Publications
\section*{Publications}
\vspace{-12pt}
{\footnotesize \text{*} Pre-prints, replication materials, and pre-registrations for all publications are available on \href{https://osf.io/utdaf/}{my OSF page}.}

\subsection*{Journal Articles}

  \years{[4]} \textbf{Zhou, A.} (2021). Causal effects of affordance change on communication behavior: Empirical evidence from organizational and leadership social media use. \textit{Telematics and Informatics}, \textit{59}, 101549. \doi{https://doi.org/10.1016/j.tele.2020.101549}\\
  \years{} {[SSCI, 2019 1Y/5YIF: 4.139/4.454]}\\
  \years{[3]} Xu, S., \& \textbf{Zhou, A.} (2020). Hashtag homophily in Twitter network: Examining a controversial cause-related marketing campaign. \textit{Computers in Human Behavior}, \textit{102}, 87-96. \doi{https://doi.org/10.1016/j.chb.2019.08.006}\\
  \years{} {[SSCI, 2019 1Y/5YIF: 5.003/5.696]}\\
  \years{[2]} Jaidka, K., \textbf{Zhou, A}., \& Lelkes, Y. (2019). Brevity is the soul of Twitter: The constraint affordance and political discussion. \textit{Journal of Communication}, \textit{69}(4), 345-372. \doi{https://doi.org/10.1093/joc/jqz023}\\
  \years{} {[SSCI, 2019 1Y/5YIF: 4.846/7.175]}\\
  \years{} {\textbf{[Lead Article] [Media Coverage: \href{https://www.washingtonpost.com/politics/2019/09/17/twitter-got-somewhat-more-civil-when-tweets-doubled-length-heres-how-we-know}{Washington Post}, \href{https://www.washingtonexaminer.com/opinion/twitter-conversations-have-improved-but-theres-a-better-way-to-talk-to-each-other}{Washington Examiner}, \href{https://phys.org/news/2019-09-character-limit-twitter-civil.html}{Phys.org}]}\\
  \years{[1]} \textbf{Zhou, A.} (2019). Bring publics back into networked public relations research: A dual-projection approach for network ecology. \textit{Public Relations Review}, \textit{45}(4), 101772. \doi{https://doi.org/10.1016/j.pubrev.2019.03.004}\\
  \years{} {[SSCI, 2019 1Y/5YIF: 2.321/2.232]}\\
  \years{} {\textbf{[2020 PRIDE Article of the Year Award, Public Relations Division, NCA]}}

\subsection*{Working Papers}

\years{[11]} \textbf{Zhou, A.}, \& Dias, N. (In Preparation). \textit{Researcher ideology.}\\
\years{[10]} \textbf{Zhou, A.}, \& Xu, S. (In Preparation). \textit{Affordances for mediated dialogue.}\\
\years{[9]} \textbf{Zhou, A.}, Jaidka, K., \& Lelkes, Y. (In Preparation). \textit{Reply \& reactions.}\\
\years{[8]} Tsai, W.H. S., \textbf{Zhou, A.}, \&  Men, R. L. (In Preparation). \textit{Chatbots' relational design.}\\
\years{[7]} Men, R. L., \textbf{Zhou, A.}, \& Tsai, W.H. S. (In Preparation). \textit{Chatbots for relationship building.}\\
\years{[6]} \textbf{Zhou, A.} (In Preparation). \textit{Public-public relationships.}\\
\years{[5]} \textbf{Zhou, A.}, \& Yang, A. (In Preparation). \textit{Movement spillover.}\\
\years{[4]} Jaidka, K., \textbf{Zhou, A.}, Lelkes, Y., Egelhofer, J., \& Lecheler, S. (R\&R). \textit{Deliberation design.}\\
\years{[3]} \textbf{Zhou, A.} (Under Review). \textit{CSR discourse on LGBTQ advocacy.} \doi{https://doi.org/10.31219/osf.io/gz7bw}\\
\years{[2]} Wang, R., \textbf{Zhou, A.}, \& Bar, F. (Under Review). \textit{Police brutality in Hong Kong.}\\
\years{[1]} \textbf{Zhou, A.}, \& Xu, S. (R\&R). \textit{Affordances in digital public relations.} \doi{https://doi.org/10.31235/osf.io/uzhk9}

\subsection*{Book Reviews}

  \years{[2]} \textbf{Zhou, A.} (2018). Review of \textit{Society \& the Internet: How networks of information and communication are changing our lives}, edited by Mark Graham \& William H. Dutton. \textit{Information, Communication \& Society, 21}(12), 1769-1771. \doi{https://doi.org/10.1080/1369118X.2018.1465577}\\
  \years{[1]} \textbf{Zhou, A.} (2017). Review of \textit{\#Republic: Divided democracy in the age of social media}, by Cass R. Sunstein. \textit{Journal of Communication, 67}(6), E12–E14. \doi{https://doi.org/10.1111/jcom.12344}

\subsection*{Refereed Conference Presentations}

%\years{[18]} \textbf{Zhou, A.}, \& González-Bailón, S. (2021). \textit{Digital news consumption leading up to the U.S. 2020 election}. International Communication Association (Journalism Studies Division), Virtual.\\
%\years{[17]} \textbf{Zhou, A.}, \& Xu, S. (2021). \textit{Is mediated dialogue dead yet?: How media affordances affect organization-public relationship building}. International Communication Association (Public Relations Division), Virtual.\\
%\years{[16]} \textbf{Zhou, A.} (2021). \textit{Causal effects of affordance change on communication behavior: Empirical evidence from organizational and leadership social media use}. International Communication Association (Communication and Technology Division), Virtual.\\
%\years{[15]} \textbf{Zhou, A.}, \& Dias, N. (2021). \textit{You won’t speak for me: Researcher partisanship as a source of recruitment and response bias}. Midwest Political Science Association (Public Opinion Section), Virtual.\\
%\years{[14]} Yue, C. A., Fan, Q., Vielledent, M., Men, R. L., \& \textbf{Zhou, A.} (2021). \textit{Leadership going social: How U.S. nonprofit executives engage publics on Twitter}. International Public Relations Research Conference, Virtual.\\
%\years{[13]} \textbf{Zhou, A.} (2021). \textit{Communicating corporate LGBTQ advocacy: A computational comparison of the global CSR discourse}. International Public Relations Research Conference, Virtual.\\
\years{[12]} \textbf{Zhou, A.}, \& Yang, A. (2020). \textit{Bridging inter-movement networks: A structural analysis of movement spillover}. National Communication Association (Political Communication Division), Virtual.\\
\years{[11]} Wang, R., \textbf{Zhou, A.}, \& Bar, F. (2020). \textit{Identifying network mechanisms underlying the use of \#HongKongPoliceBrutality}. International Network for Social Network Analysis (SunBelt), Virtual.\\
\years{[10]} \textbf{Zhou, A.} (2020). \textit{Relationship management in an organizational network ecology: Toward the concept of public-public relationships}. International Communication Association (Public Relations Division), Virtual.\\
\years{[9]} Jaidka, K., \textbf{Zhou, A.}, Lelkes, Y., Egelhofer, J., \& Lecheler, S. (2020). \textit{This SIDE of us: Experiments to improve deliberation by manipulating social media affordances}. International Communication Association (Computational Methods Interest Group), Virtual. [Also Presented at IC2S2 2020]\\
\years{[8]} \textbf{Zhou, A.}, \& Xu, S. (2019). \textit{Expanding and repositioning the ``ease of interface'' dialogic principle: The role of affordances in digital dialogue and engagement}. International Communication Association (Public Relations Division), Washington, DC.\\
\years{} \textbf{[Robert Heath Award] [Top Faculty Paper Award, 1$^{st}$ Place]}\\
\years{[7]} \textbf{Zhou, A.}, \& González-Bailón, S. (2019). \textit{Revisiting ideological segregation on the web: A block model approach to audience network data}. International Communication Association (Computational Methods Interest Group), Washington, DC.\\
\years{[6]} Jaidka, K., \textbf{Zhou, A.}, \& Lelkes, Y. (2019). \textit{The effect of technological affordances on the online political sphere: The case of Twitter character limit switch}. International Communication Association (Political Communication Division), Washington, DC. [Also Presented at SPSA 2019 \& APSA 2019]\\
\years{[5]} \textbf{Zhou, A.} (2019). \textit{Networks of publics overlap: A network measure for social media campaign management}. International Public Relations Research Conference, Orlando, FL.\\
\years{[4]} \textbf{Zhou, A.}, \& Xu, S. (2018). \textit{Bigger playground, better dialogues?: A large-scale examination of corporate Twitter communication in the 280-character era}. National Communication Association (Public Relations Division), Salt Lake City, UT.\\
\years{} \textbf{[Top Student Paper Award, 1$^{st}$ Place]}\\
\years{[3]} \textbf{Zhou, A.} (2018). \textit{Bring publics back into networked public relations research: A dual-projection approach for network ecology}. International Communication Association (Public Relations Division), Prague, Czech Republic.\\
\years{[2]} \textbf{Zhou, A.}, \& Khan, A. (2017). \textit{Altruistic or ``pinkwashed'' CSR discourse: An analysis of corporate and non-profit LGBTQ values}. International Communication Association (Public Relations Division), San Diego, CA.\\
\years{[1]} \textbf{Zhou, A.} (2016). \textit{The emerging values of global CSR discourse: A cross-national big-data analysis of Fortune Global 500 companies' LGBTQ values}. National Communication Association (Public Relations Division), Philadelphia, PA.\\
\years{} \textbf{[Top Student Paper Award, 3$^{rd}$ Place]}

% Invited Presentations
\section*{Invited Presentations}

  \years{2019} Invited Panelist, \textit{How Far Have We Come?: Public Relations Theory Building and Development}, International Communication Association.\\
  \years{2019} Invited Talk, \textit{Advancing the Network Ecology Approach to Public Relations}, Invited by Adam Saffer, University of North Carolina at Chapel Hill.\\
  \years{2019} Invited Talk, \textit{Advancing the Network Ecology Approach to Public Relations}, Invited by Maureen Taylor, University of Tennessee.\\
  \years{2016} Invited Talk, \textit{Automated Text Analysis with Topic Modeling}, Invited by Patricia Riley, University of Southern California.

% Teaching
\section*{Teaching}

\subsection*{Teaching Areas}

  \years{-} Computational Social Science: Data Mining/Visualization, Social Computing, Networks\\
  \years{-} Public Relations Theory, Method, and Campaign\\
  \years{-} Audience Behavior, News Consumption, Ideological Segregation\\
  \years{-} Digital Methods, Quantitative Research Methods, Causal Inference

\subsection*{Teaching Training and Honors}

  \years{2020} Teaching Certificate, Center for Teaching and Learning, UPenn\\
  \years{2019} Boot Camp on Online Teaching, Center for Teaching and Learning, UPenn\\
  \years{2018} Teaching Qualification, Center for Teaching and Learning, UPenn

\subsection*{Teaching Experiences}

  \years{2020} COMM 313, Computational Text Analysis, University of Pennsylvania\\
  \years{} Teaching Fellow for Matthew O'Donnell, 50 Students\\
  \years{} Manage Weekly Lab Sessions on Text Analysis in Python\\
  \years{2019} COMM 226, Intro to Political Communication, University of Pennsylvania\\
  \years{} Teaching Fellow for Doron Taussig, 70 Students\\
  \years{} One Guest Lecture on \textit{Political Polarization}\\
  \years{2019} COMM 407, Understanding Social Networks, University of Pennsylvania\\
  \years{} Teaching Fellow for Sandra González-Bailón, 22 Students\\
  \years{} Manage Weekly Lab Sessions on Social Network Analysis in Gephi\\
  \years{2019} COMM 130, Media Industries and Society, University of Pennsylvania\\
  \years{} Teaching Fellow for Lee McGuigan, 70 Students\\
  \years{} One Guest Lecture on \textit{The Contemporary Video Game Industry}\\
  \years{2019} COMM 284, Public Relations Research, Measurement, and Evaluation, Drexel University\\
  \years{} Guest Lecturer Invited by Hyunmin Lee, 20 Students\\
  \years{} Two Guest Lectures on \textit{Public Relations \& Social Networks}

% Grant Experiences
\section*{Grant Experiences}

  \years{2020} PI for \textit{Digital Inequalities in Organizational Listening}\\
  \years{} The Arthur W. Page Center Page/Johnson Legacy Scholar Grant (\$9,900)\\
  \years{} Not Funded. Co-PI: Rita Linjuan Men \& Tom Kelleher\\
  \years{2020} Co-PI for \textit{Harnessing the Power of Chatbots for Organizational Social Listening}\\
  \years{} The Arthur W. Page Center Page/Johnson Legacy Scholar Grant (\$5,500)\\
  \years{} Funded. PI: Rita Linjuan Men; Co-PI: Wanhsiu Sunny Tsai\\
  \years{2019} Research Fellow for \textit{Effects of Social Network Affordances on Political Discussion Health}\\
  \years{} Facebook Integrity Foundational Research (\$100,000)\\
  \years{} Funded. PI: Yphtach Lelkes\\
  \years{2018-20} Research Fellow for \textit{Digital News and the Consumption of Information Online}\\
  \years{} National Science Foundation Grant (\$130,000)\\
  \years{} Funded. PI: Sandra González-Bailón

% Academic Experiences
\section*{Academic Experiences}

  \years{2020}Research Fellow for Yphtach Lelkes: DIG Research Group\\
  \years{2018}The Annenberg Summer Institute for Methods and Statistics (ASIMS)\\
  \years{2018-21}Research Fellow for Sandra González-Bailón: DiMeNet Research Group\\
  \years{2017-18}Research Fellow for Damon Centola: Network Dynamics Group\\
  \years{2016-17}Research Assistant for Jay Wang: Center on Public Diplomacy\\
  \years{2015-17}Research Assistant for Patricia Riley: Scenario Lab\\
  \years{2015-17}Research Assistant for Joe Saltzman: The Norman Lear Center\\
  \years{2012-14}Research Assistant for Jianbin Jin: Tsinghua-RenRen Social Media Lab\\
  \years{2012-14}Research Assistant for Guanpeng Dong: IPRSC

% Services
\section*{Services}

\subsection*{Review Services}
\vspace{-9pt}
{\footnotesize \text{*} Detailed review history can be accessed on \href{https://publons.com/researcher/1698569/alvin-zhou/}{my Publon page}.}
\vspace{12pt}

  \years{2019-} Ad-hoc Reviewer (by alphabetical order):\\
  \years{} \hspace*{2em} \textit{Convergence}\\
  \years{} \hspace*{2em} \textit{Journal of Communication Management}\\
  \years{} \hspace*{2em} \textit{Political Communication}\\
  \years{} \hspace*{2em} \textit{Public Relations Review}\\
  \years{2017-} ICA Divisions: Computational Methods, Political Communication, \& Public Relations\\
  \years{2016-} NCA Divisions: Political Communication \& Public Relations

\subsection*{Administrative and Conference Services}
  
  \years{2021-23} Student and Early Career Representative, Public Relations Division, ICA\\
  \years{2020-22} Social Media Committee, Public Relations Division, NCA\\
  \years{2019-20} Ad Hoc Fundraising Committee, Public Relations Division, NCA\\
  \years{2018-22}Group Coordinator, DiMeNet Research Group, University of Pennsylvania\\
  \years{2015-17}IJPC Manager, Norman Lear Center, University of Southern California

% Graduate Coursework

\section*{Graduate Coursework}

\subsection*{Computational Social Science and Advanced Statistics}

  \years{} Data Visualization (UPenn Annenberg, Sandra González-Bailón)\\
  \years{} Causal Inference and Bayesian Inference (UPenn Political Science, Daniel Hopkins)\\
  \years{} Research Methods for a Fragmented Media Environment (UPenn Annenberg, Yphtach Lelkes)\\
  \years{} Research Seminar on Computational Social Science (UPenn Annenberg, Damon Centola)\\
  \years{} Experimental Design and Issues in Causality (UPenn Annenberg, Diana Mutz)\\
  \years{} Modern Data Mining (Wharton, Linda Zhao)\\
  \years{} Causal Inference (Wharton, Dylan Small)\\
  \years{} Observational Studies (Wharton, Dylan Small)\\
  \years{} Modern Regression and Machine Learning (Wharton, Richard Berk)\\
  \years{} Nonparametric and Log-Linear Models (Wharton, Paul Rosenbaum)\\
  \years{} Applied Regression and Analysis of Variance (Wharton, Paul Rosenbaum)\\
  \years{} Modern Statistics for Social and Behavioral Sciences (USC Psychology, Rand Wilcox)

\subsection*{Strategic Communication}

  \years{} Theories of Organizational Communication (USC Annenberg, Patricia Riley)\\
  \years{} Research and Evaluation for Communication Campaigns (UPenn Annenberg, Robert Hornik)\\
  \years{} Strategic Public Relations (USC Annenberg, Dotty Diemer)\\
  \years{} Public Relations Theory, Research, and Campaigns (USC Annenberg, Robert Kozinets)\\
  \years{} Multimedia Content Creation for Strategic Public Relations (USC Annenberg, Clint Schaff)\\
  \years{} Economic Foundations of Strategic Public Relations (USC Annenberg, Burghardt Tenderich)\\
  \years{} Ethical Foundations of Strategic Public Relations (USC Annenberg, Daren Brabham)\\
  \years{} Public Relations Writing (USC Annenberg, Ron Grover)

\subsection*{Political Communication}

  \years{} Digital News Consumption (UPenn Annenberg, Sandra González-Bailón)\\
  \years{} Polarization and Partisan Discord (UPenn Annenberg, Yphtach Lelkes)\\
  \years{} Ideological Segregation (UPenn Annenberg, Sandra González-Bailón)\\
  \years{} Affordances and Digital Media (UPenn Annenberg, Yphtach Lelkes)\\
  \years{} Social Psychology in Communication (UPenn Annenberg, Joseph Cappella)\\
  \years{} Communication Research (UPenn Annenberg, Robert Hornik)\\
  \years{} Digital Inequalities (UPenn Annenberg, Julia Ticona)

% Professional Experiences  

\section*{Professional Experiences}

  \years{2014-16} Journalist, Vista Story, Beijing\\
%  [.2cm]{\small\textit{I wrote dozens of news articles on politics and public affairs for \href{https://weibo.com/vistastory}{Vista Story}, the best-selling news magazine in China. My most shared work includes: \href{https://goo.gl/HrPLCf}{Chinese Bullies Abroad: When Adolescent Misbehavior Breaks American Laws}; \href{https://mp.weixin.qq.com/s/VRI--oVEJGC8m2isrgKvdQ}{The Rainbow Flag: US Supreme Court Legalizes Same-sex Marriage}; \href{https://mp.weixin.qq.com/s/MTwhcEFCdQV5XQ6MbuCpgg}{Caitlyn Jenner: The Transition of the Olympics Decathlete}; \href{https://goo.gl/HRzxQS}{Entrepreneur Li KeQiang}; \href{https://mp.weixin.qq.com/s/44ho_gGsIeMl4O_bT9iNew}{HandJob Angels: Volunteers Help Release the Sexual Desires of the Handicapped}; \href{https://goo.gl/QWctZa}{Torture Report: The Dark Side of C.I.A.}; \href{https://weibo.com/1323527941/AAXVOakBL?from=page_1002061323527941_profile&wvr=6&mod=weibotime}{Flight Safety in the Aftermath of MH370}.}}\\[.2cm]
   \years{2013} Broadcaster Intern, Xinhua News Agency, Beijing\\
   \years{2013} Reporter Intern, News Probe, China Central Television, Beijing\\
   \years{2013} Account Executive Intern, BlueFocus Communication Group, Beijing\\
   \years{2012-13} Vice Chairman, Project Management Association, Tsinghua University\\
   \years{2012-13} Vice Minister, Tsinghua Student Union, Tsinghua University
%   \years{2012}Director, Cinematographer, \& Film Editor, Memorial Film for Zhuji High School’s Centennial, Zhuji, Zhejiang. \href{http://video.tudou.com/v/XMjE5MTY0MTYwMA==.html?bid=03\&pid=02\&resourceId=0_03_05_02}{\textit{TuDou}}

% % Skills

\section*{Skills}

  \years{Language} Mandarin Chinese (native), R, Python, \LaTeX, SPSS, STATA\\
  \years{Media} Final Cut Pro, Sony Vegas Pro 12, Adobe Illustrator, \& Adobe Photoshop, all proficient with years of professional multimedia production experiences

%\newpage
% References
%\section*{References}
%
%\textbf{Sandra González-Bailón}\\
%Associate Professor\\
%The Annenberg School\\
%University of Pennsylvania\\
%Email: \href{mailto:sgonzalezbailon@asc.upenn.edu}{sgonzalezbailon@asc.upenn.edu}\\[.5cm]
%\textbf{Aimei Yang}\\
%Assistant Professor\\
%The Annenberg School\\
%University of Southern California\\
%Email: \href{mailto:aimei.yang@usc.edu}{aimei.yang@usc.edu}\\[.5cm]
%\textbf{Yphtach Lelkes}\\
%Assistant Professor\\
%The Annenberg School\\
%University of Pennsylvania\\
%Email: \href{mailto:yphtach.lelkes@asc.upenn.edu}{yphtach.lelkes@asc.upenn.edu}

\end{document}